Computation and comparison of the stable northeastern United States marine boundary layer

### 2020-12-08 Paper/methodology.tex
Small changes to implicit viscous description

AMR-Wind solves the incompressible Navier-Stokes equations and is generalized to
handle variable density and viscosity. Additionally, scalar transport equations
can be solved, such as potential temperature or turbulence models. The
discretization in AMR-Wind is based on the approximate projection method used in
IAMR \cite{almgren1998conservative} and incflo \cite{sverdrup2018highly}. It is
a semi-staggered scheme where the velocity and scalar variables are located at
cell centers and pressure is located at nodes. Pressure is also staggered in
time so that pressure and the pressure gradient (located at cell centers) are at
time $n+1/2$.  The time discretization is handled with a Crank Nicolson
approach where the right-hand side of the system of equations is evaluated at
time $n+1/2$. The advection term is handled explicitly using an upwind
finite-volume method. There are multiple options within AMR-Wind, but in this
paper only the high-order Godunov Piecewise Parabolic Method (PPM) is used
\cite{Colella1984}. The advection terms are projected to face centers at $n+1/2$
and are corrected using an exact MAC projection~\cite{almgren1998conservative},
which guarantees a divergence-free flow. The diffusion terms can be handled
explicitly, semi-implicitly, or implicitly and are spatially discretized using a
second-order central difference formula.  For the simulations in this paper, we
use a fully implicit scheme, as the variable viscosity from the eddy viscosity
may cause time step restrictions. After the scalar equations and the momentum
equations are advanced in time, a nodal projection is used to approximately
correct the velocity field to make it divergence free.  The nodal projection is
based on a node centered finite element method \cite{almgren1998conservative}.

>>>>

AMR-Wind solves the incompressible Navier-Stokes equations and is generalized to
handle variable density and viscosity. Additionally, scalar transport equations
can be solved, such as potential temperature or turbulence models. The
discretization in AMR-Wind is based on the approximate projection method used in
IAMR \cite{almgren1998conservative} and incflo \cite{sverdrup2018highly}. It is
a semi-staggered scheme where the velocity and scalar variables are located at
cell centers and pressure is located at nodes. Pressure is also staggered in
time so that pressure and the pressure gradient (located at cell centers) are at
time $n+1/2$.  The time discretization is handled with a Crank Nicolson
approach where the right-hand side of the system of equations is evaluated at
time $n+1/2$. The advection term is handled explicitly using an upwind
finite-volume method. There are multiple options within AMR-Wind, but in this
paper only the high-order Godunov Piecewise Parabolic Method (PPM) is used
\cite{Colella1984}. The advection terms are projected to face centers at $n+1/2$
and are corrected using an exact MAC projection~\cite{almgren1998conservative},
which guarantees a divergence-free flow. The diffusion terms can be handled
explicitly, semi-implicitly, or implicitly and are spatially discretized using a
second-order central difference formula.  For the simulations in this paper, we
use an implicit scheme for the viscous terms, as the variable viscosity from the eddy viscosity
may cause time step restrictions. After the scalar equations and the momentum
equations are advanced in time, a nodal projection is used to approximately
correct the velocity field to make it divergence free.  The nodal projection is
based on a node centered finite element method \cite{almgren1998conservative}.
